### 2022-04-04 papers.tex

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{Blindsight is also 2021}

@@

\addpaper
    {brainfuck++: a much needed extension to brainfuck}
    {Cédric Ho Thanh}
    {Keywords: Programing langage, brainfuck, concurrency, machine learning}
    {SIGBOVIK_2022_paper_3995}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addpaper
    {Improved Data and Instruction Locality in Long Division}
    {Isaac Grosof, Isaac Grosof}
    {Keywords: performance, division, locality, data, instruction}
    {SIGBOVIK_2022_paper_0463}
    {0cm}
    {}
\addpaper
    {Real-Time Foliage Simulation}
    {Emma Liu, Sanjay Salem, Daniel Zeng, Mia Tang, Hesper Yin, George Ralph, Anne He, Max Slater}
    {Keywords: real-time, simulation, graphics, rendering}
    {SIGBOVIK_2022_paper_0683}
    {0cm}
    {}
%\addreview
%    {SIGBOVIK_2021_review_5}
%    {0cm}

@@

\addtrack
    {}{Climate Science}

@@

\addpaper
    {On the Possibilities and Challenges of Organic UAV-Assisted MEC}
    {}
    {Keywords:chick-a-dee, caw caw, chirp chirp, hoot hoot}
    {SIGBOVIK_2022_paper_9501}
    {0cm}
    {S. Wallow, Cardi Nalle, Robin, P. Cock, and Sky Lark}

\addpaper
    {A Patriotic Analysis of Programming Paradigms}
    {Jacob Weiner}
    {Keywords: Patriotism, Constitution, Dependent Type Theory}
    {SIGBOVIK_2022_paper_1689}
    {0cm}
    {}
\addpaper
    {Solving Double Execution of Java’s paint() Method by Counting Down to the Heat Death of the Universe (plus language compendium)}
    {Braden Oh, Vedaant Kuchhal, Junseok Kang, Andrew Mascillaro, Justin Kunimune, Shashank Swaminathan, Devlin Ih, Elias Gabriel, Audrey Lee, Colin Snow, Hyunkyung Rho, Ben Morris, Solomon Greenberg, Mahima Beltur, Anusha Datar, Jonathan Kelley, Pranavi Boyalakuntla, Xander Hughes, Devyn Oh, Aidan Schmitigal}
    {Keywords: Efficient, Effective, Compendium, Languages, Heat death, Overkill}
    {SIGBOVIK_2022_paper_1777}
    {0cm}
    {}
\addpaper
    {Multiplication by repeated addition, with fraction handling.}
    {Jim McCann}
    {Keywords: multiplication, punctuation: *, C++, source code}
    {SIGBOVIK_2022_paper_1824}
    {0cm}
    {}
\addpaper
    {Objective Correlation Metrics for Quality of Code Estimation}
    {Eleftheria Chatziargyriou and Konstantinos Kanavouras}
    {Keywords: programming, quality, code, objective}
    {SIGBOVIK_2022_paper_1957}
    {0cm}
    {}

@@

\addtrack
    {}{Followup Track}
\addpaper
    {(Un)helper functions}
    {Kevin Smith and Bernhard Egger}
    {Keywords: algorithms, algorithm patent trolling, cite us please!}
    {SIGBOVIK_2022_paper_2133}
    {0cm}
    {}

\addtrack
    {}{``Type'' Track}
%\addpaper
%    {Investigations and Difficulties in Real - to -Sim}
%    {Sashank Tirumala}
%    {Keywords: Robotics, Machine Learning, Deep Learning, Reinforcement Learning}
%    {SIGBOVIK_2022_paper_3472}
%    {0cm}
%    {}

\addtrack
    {}{(Psycho)metrics Track}
\addpaper
    {Quadruple-Blind Peer Review}
    {Yuriko Shu}
    {Keywords: Peer Review, Quadruple Blind Reviewing, Bias Reduction}
    {SIGBOVIK_2022_paper_3958}
    {0cm}
    {}
\addpaper
    {A sometimes-accurate O(1) search algorithm}
    {A College Freshman}
    {Keywords:fast, search, search algorithm, searching algorithm, searching, how many ways can i say search algorithm}
    {SIGBOVIK_2022_paper_4297}
    {0cm}
    {}

\addreview
    {SIGBOVIK_2021_review_1}
    {0cm}

\addtrack
    {}{Math}

@@

\addreview
    {SIGBOVIK_2021_review_4}
    {0cm}

\addpaper
    {A 23 MW data centre is all you need}
    {Samuel Albanie, Dylan Campbell and João Henriques}
    {Keywords: machine learning, prophecy, Molly}
    {SIGBOVIK_2022_paper_4719}
    {0cm}
    {}
\addpaper
    {Optimal degeneracy through OwO based variable names}
    {Fwans Skawman}
    {Keywords: OwO, What's, This}
    {SIGBOVIK_2022_paper_4751}
    {0cm}
    {}
\addtrack
    {}{Hardware}

@@

\addpaper
    {Wearable RF-shield repositories}
    {Abe Wits and J. Mijn}
    {Keywords: security, wifi, cable}
    {SIGBOVIK_2022_paper_9009}
    {0cm}
    {}

\addpaper
    {A Third Thorough Investigation of the Degree to which the COVID-19 Pandemic has Enabled Subpar-Quality Papers to Make it into SIGBOVIK, by Reducing the Supply of Authors Willing to Invest the Necessary Effort to Produce High-Quality Papers}
    {Shalin Shah}
    {Keywords: SIGBOVIK, COVID-19, Lazy, Low-Effort}
    {SIGBOVIK_2022_paper_5584}
    {0cm}
    {}
\addpaper
    {EBMP: Efficient Bitmap Encodings on Ethereum Virtual Machines}
    {0XMOSTIMA, Yunsong Liu and Peiyuan Liao}
    {Keywords: still image coding, blockchain, smart contracts, non fungible tokens}
    {SIGBOVIK_2022_paper_5649}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addpaper
    {Everybody Clap Your Hands: The Cha Cha Slide is Turing Complete}
    {Harrison Goldstein}
    {Keywords: Turing complete, Cha Cha Slide, line dance, party, complexity}
    {SIGBOVIK_2022_paper_5708}
    {0cm}
    {\badges{\badge{pagenumbers}}}

\addtrack{}{(Meta)physics}
%\fancypagestyle{fancypyramid}{\fancyheadoffset[roh]{0.75in}}
\addpaper
    {SEGA-NVidia 32esque Advertisements}
    {Jim McCann}
    {Keywords: sega, nvidia, 3D 3D, rtesque}
    {SIGBOVIK_2022_paper_6593}
    {0cm}
    {}
\addpaper
    {Edward, edMUnD & Edwin: Line-Based Text Editing for the 21st Century}
    {Natalia Posting and Katie Wolfe}
    {Keywords: line-based text editing, line-cringe text editing, synergy}
    {SIGBOVIK_2022_paper_6729}
    {0cm}
    {}
\addpaper
    {Baby Sharks are More than Sharks . They are Earworms Sung More than Happy Birthday Perhaps}
    {Kofi Oduro}
    {Keywords: Sharks, Happy Birthday, Swimming Shark Problem, Shark Week, billions, humans, kindergarten, PRe-K}
    {SIGBOVIK_2022_paper_6744}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addreview
    {SIGBOVIK_2021_review_2}
    {0cm}

\addtrack
    {}{Definitely Finite Track}

%\addpaper
%    {AI is a Really, Really, Really Bad Idea}
%    {Molly de Blanc}
%    {Keywords: artificial intelligence, ethics, machine learning}
%    {SIGBOVIK_2021_paper_10}
%    {0cm}
%    {}

\addpaper
    {Destructive Logic}
    {Runming Li}
    {Keywords: logic, constructive logic, destructive logic, type theory}
    {SIGBOVIK_2022_paper_6801}
    {0cm}
    {}

\addpaper
    {On Ruinment: Ruination Theory and its Consequents}
    {Luna Tascheter}
    {Ruination Theory, Ruinment, T0T4L PWN4G∃, Category Theory, Adam Conover, Adam Sandler, Hallmark, Waste of Paper, Orange}
    {SIGBOVIK_2022_paper_6808}
    {0cm}
    {}

\addtrack
    {}{Recursive Track}
\addpaper
    {Overlap-Maximal Graph Labelings: Graph Labelings with Non-Disjoint Vertex and Edge Sets (and how they can be used for encryption, poetry, and breaking mathematics)}
    {Gabriel Chuang}
    {Keywords: Graph Theory, Cryptography, Fox in Socks by Dr. Seuss}
    {SIGBOVIK_2022_paper_6809}
    {0cm}
    {}

\addpaper
    {Using deep CNNs to prove that I look better than Tom Cruise and Shah Rukh Khan combined}
    {Sagar Bharadwaj Kalasibail Seetharam}
    {Keywords: CNN, Machine Learning, Image Compression}
    {SIGBOVIK_2022_paper_6854}
    {0cm}
    {}
\addpaper
    {Analysis of A New Error Calculation Technique}
    {Jevin Tong} 
    {Keywords: late, erroneous, hackneyed}
    {SIGBOVIK_2022_paper_7011}
    {0cm}
    {\badges{\badge{pagenumbers}}}

\addpaper
    {Functorial wrappers for high-dimensional classification algorithms}
    {James Carzon}
    {Keywords: forgetful functor, classification, high dimensional data}
    {SIGBOVIK_2022_paper_7603}
    {0cm}
    {}

@@

\addpaper
    {Redundant Coupling}
    {Peter Kos}
    {Keywords: software engineering, coupling, cohesion, rust, martin fowler, fowler, james gosling, donald knuth}
    {SIGBOVIK_2022_paper_8888}
    {0cm}
    {}
\addpaper
    {A Machine Learning Approach To Classifying Cuteness}
    {Anoushka Shrivastava}
    {Keywords: machine learning, classification, cuteness}
    {SIGBOVIK_2022_paper_9240}
    {0cm}
    {}

\addpaper
    {this is not a review}
    {Huilian Sophie Qiu}
    {Keywords: this, is, not, review}
    {SIGBOVIK_2022_paper_9376}
    {0cm}
    {}

@@

>>>>

\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}
\addproceedings{TODO: Tell next year's committee that they should probably avoid further milking of the blindsight joke}

@@

\addpaper
    {brainfuck++: a much needed extension to brainfuck}
    {Cédric Ho Thanh}
    {Keywords: Programing langage, brainfuck, concurrency, machine learning}
    {SIGBOVIK_2022_paper_3995}
    {0cm}
    {\badges{\badge{pagenumbers}}}
%\addreview
%    {SIGBOVIK_2021_review_5}
%    {0cm}

@@

\addpaper
    {Solving Double Execution of Java’s paint() Method by Counting Down to the Heat Death of the Universe (plus language compendium)}
    {Braden Oh, Vedaant Kuchhal, Junseok Kang, Andrew Mascillaro, Justin Kunimune, Shashank Swaminathan, Devlin Ih, Elias Gabriel, Audrey Lee, Colin Snow, Hyunkyung Rho, Ben Morris, Solomon Greenberg, Mahima Beltur, Anusha Datar, Jonathan Kelley, Pranavi Boyalakuntla, Xander Hughes, Devyn Oh, Aidan Schmitigal}
    {Keywords: Efficient, Effective, Compendium, Languages, Heat death, Overkill}
    {SIGBOVIK_2022_paper_1777}
    {0cm}
    {}
\addtrack
    {}{Climate Science}

@@

\addpaper
    {On the Possibilities and Challenges of Organic UAV-Assisted MEC}
    {S. Wallow, Cardi Nalle, Robin, P. Cock, and Sky Lark}
    {Keywords:chick-a-dee, caw caw, chirp chirp, hoot hoot}
    {SIGBOVIK_2022_paper_9501}
    {0cm}
    {}
\addtrack
    {}{Aesthetics}

\addpaper
    {Real-Time Foliage Simulation}
    {Emma Liu, Sanjay Salem, Daniel Zeng, Mia Tang, Hesper Yin, George Ralph, Anne He, Max Slater}
    {Keywords: real-time, simulation, graphics, rendering}
    {SIGBOVIK_2022_paper_0683}
    {0cm}
    {}

\addpaper
    {Using deep CNNs to prove that I look better than Tom Cruise and Shah Rukh Khan combined}
    {Sagar Bharadwaj Kalasibail Seetharam}
    {Keywords: CNN, Machine Learning, Image Compression}
    {SIGBOVIK_2022_paper_6854}
    {0cm}
    {}

\addpaper
    {EBMP: Efficient Bitmap Encodings on Ethereum Virtual Machines}
    {0XMOSTIMA, Yunsong Liu and Peiyuan Liao}
    {Keywords: still image coding, blockchain, smart contracts, non fungible tokens}
    {SIGBOVIK_2022_paper_5649}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addpaper
    {A Machine Learning Approach To Classifying Cuteness}
    {Anoushka Shrivastava}
    {Keywords: machine learning, classification, cuteness}
    {SIGBOVIK_2022_paper_9240}
    {0cm}
    {}

@@

\addtrack
    {}{Best Practices}
%\addpaper
%    {Investigations and Difficulties in Real - to -Sim}
%    {Sashank Tirumala}
%    {Keywords: Robotics, Machine Learning, Deep Learning, Reinforcement Learning}
%    {SIGBOVIK_2022_paper_3472}
%    {0cm}
%    {}
\addpaper
    {Quadruple-Blind Peer Review}
    {Yuriko Shu}
    {Keywords: Peer Review, Quadruple Blind Reviewing, Bias Reduction}
    {SIGBOVIK_2022_paper_3958}
    {0cm}
    {}
\addpaper
    {Optimal degeneracy through OwO based variable names}
    {Fwans Skawman}
    {Keywords: OwO, What's, This}
    {SIGBOVIK_2022_paper_4751}
    {0cm}
    {}

\addpaper
    {Multiplication by repeated addition, with fraction handling.}
    {Jim McCann}
    {Keywords: multiplication, punctuation: *, C++, source code}
    {SIGBOVIK_2022_paper_1824}
    {0cm}
    {}
\addpaper
    {Objective Correlation Metrics for Quality of Code Estimation}
    {Eleftheria Chatziargyriou and Konstantinos Kanavouras}
    {Keywords: programming, quality, code, objective}
    {SIGBOVIK_2022_paper_1957}
    {0cm}
    {}

\addpaper
    {(Un)helper functions}
    {Kevin Smith and Bernhard Egger}
    {Keywords: algorithms, algorithm patent trolling, cite us please!}
    {SIGBOVIK_2022_paper_2133}
    {0cm}
    {}

\addtrack
    {}{Mathematics}

\addpaper
    {Improved Data and Instruction Locality in Long Division}
    {Isaac Grosof, Isaac Grosof}
    {Keywords: performance, division, locality, data, instruction}
    {SIGBOVIK_2022_paper_0463}
    {0cm}
    {}

@@

\addtrack
    {}{Hardware}

@@

\addpaper
    {Wearable RF-shield repositories}
    {Abe Wits and J. Mijn}
    {Keywords: security, wifi, cable}
    {SIGBOVIK_2022_paper_9009}
    {0cm}
    {}
\addpaper
    {SEGA-NVidia 32esque Advertisements}
    {Jim McCann}
    {Keywords: sega, nvidia, 3D 3D, rtesque}
    {SIGBOVIK_2022_paper_6593}
    {0cm}
    {}

\addtrack{}{A Brief Musical Interlude}
%\fancypagestyle{fancypyramid}{\fancyheadoffset[roh]{0.75in}}
\addpaper
    {Baby Sharks are More than Sharks . They are Earworms Sung More than Happy Birthday Perhaps}
    {Kofi Oduro}
    {Keywords: Sharks, Happy Birthday, Swimming Shark Problem, Shark Week, billions, humans, kindergarten, PRe-K}
    {SIGBOVIK_2022_paper_6744}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addreview
    {SIGBOVIK_2021_review_2}
    {0cm}

\addpaper
    {Everybody Clap Your Hands: The Cha Cha Slide is Turing Complete}
    {Harrison Goldstein}
    {Keywords: Turing complete, Cha Cha Slide, line dance, party, complexity}
    {SIGBOVIK_2022_paper_5708}
    {0cm}
    {\badges{\badge{pagenumbers}}}

\addtrack
    {}{Construction}

%\addpaper
%    {AI is a Really, Really, Really Bad Idea}
%    {Molly de Blanc}
%    {Keywords: artificial intelligence, ethics, machine learning}
%    {SIGBOVIK_2021_paper_10}
%    {0cm}
%    {}
\addpaper
    {Destructive Logic}
    {Runming Li}
    {Keywords: logic, constructive logic, destructive logic, type theory}
    {SIGBOVIK_2022_paper_6801}
    {0cm}
    {}

\addpaper
    {On Ruinment: Ruination Theory and its Consequents}
    {Luna Tascheter}
    {Ruination Theory, Ruinment, T0T4L PWN4G∃, Category Theory, Adam Conover, Adam Sandler, Hallmark, Waste of Paper, Orange}
    {SIGBOVIK_2022_paper_6808}
    {0cm}
    {}
\addtrack
    {}{Spoops}

@@

@@

\addpaper
    {A 23 MW data centre is all you need}
    {Samuel Albanie, Dylan Campbell and João Henriques}
    {Keywords: machine learning, prophecy, Molly}
    {SIGBOVIK_2022_paper_4719}
    {0cm}
    {}

\addtrack
    {}{Uhhhh etcetera}

\addpaper
    {A Patriotic Analysis of Programming Paradigms}
    {Jacob Weiner}
    {Keywords: Patriotism, Constitution, Dependent Type Theory}
    {SIGBOVIK_2022_paper_1689}
    {0cm}
    {}

\addpaper
    {A sometimes-accurate O(1) search algorithm}
    {A College Freshman}
    {Keywords:fast, search, search algorithm, searching algorithm, searching, how many ways can i say search algorithm}
    {SIGBOVIK_2022_paper_4297}
    {0cm}
    {}

\addpaper
    {Edward, edMUnD & Edwin: Line-Based Text Editing for the 21st Century}
    {Natalia Posting and Katie Wolfe}
    {Keywords: line-based text editing, line-cringe text editing, synergy}
    {SIGBOVIK_2022_paper_6729}
    {0cm}
    {}

\addpaper
    {A Third Thorough Investigation of the Degree to which the COVID-19 Pandemic has Enabled Subpar-Quality Papers to Make it into SIGBOVIK, by Reducing the Supply of Authors Willing to Invest the Necessary Effort to Produce High-Quality Papers}
    {Shalin Shah}
    {Keywords: SIGBOVIK, COVID-19, Lazy, Low-Effort}
    {SIGBOVIK_2022_paper_5584}
    {0cm}
    {}
\addpaper
    {this is not a review}
    {Huilian Sophie Qiu}
    {Keywords: this, is, not, review}
    {SIGBOVIK_2022_paper_9376}
    {0cm}
    {}

\addpaper
    {Functorial wrappers for high-dimensional classification algorithms}
    {James Carzon}
    {Keywords: forgetful functor, classification, high dimensional data}
    {SIGBOVIK_2022_paper_7603}
    {0cm}
    {}
\addpaper
    {Overlap-Maximal Graph Labelings: Graph Labelings with Non-Disjoint Vertex and Edge Sets (and how they can be used for encryption, poetry, and breaking mathematics)}
    {Gabriel Chuang}
    {Keywords: Graph Theory, Cryptography, Fox in Socks by Dr. Seuss}
    {SIGBOVIK_2022_paper_6809}
    {0cm}
    {}
\addpaper
    {Analysis of A New Error Calculation Technique}
    {Jevin Tong} 
    {Keywords: late, erroneous, hackneyed}
    {SIGBOVIK_2022_paper_7011}
    {0cm}
    {\badges{\badge{pagenumbers}}}

\addpaper
    {Redundant Coupling}
    {Peter Kos}
    {Keywords: software engineering, coupling, cohesion, rust, martin fowler, fowler, james gosling, donald knuth}
    {SIGBOVIK_2022_paper_8888}
    {0cm}
    {}
